---
title: "Singapore Airbnb"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
---

```{r setup, include=FALSE}

#Libraries
library(flexdashboard)
library(flextable)

# Libraries
library(DBI) 
library(RSQLite)
library(tidyr)
library(tibble)
library(stringr)
library(dbplyr)
library(dplyr, warn.conflicts = FALSE)
library(leaflet)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(tidyquant)
library(officer)
library(zoo)
library(gt)
```

```{r}
#Database Connection
con <- dbConnect(RSQLite::SQLite(), "../db/airdb.SQLite")
```

```{r}
# load host_info table 
res_host_info <- dbSendQuery(con, "select * from host_info")  
host_info <- fetch(res_host_info) 
dbClearResult(res_host_info)

# load listing table
res_listing <- dbSendQuery(con, "select * from listing")
listing <- fetch(res_listing)
dbClearResult(res_listing)
```


# Overview

Column {data-width=220}
-----------------------------------------------------------------------

### Basic Info

```{r}

```

***

Hello! Welcome to the Airbnb dashboard! Airbnb is a online marketplace for lodging, primarily for vacation rentals, and tourism activities. It allows users to connect directly with property owners and managers for affordable and flexible rentals, and allows property owners to easily monetize their properties on a much more flexible basis than conventional rentals. This dashboard was created to help people users stats, listings and reviews. The data used for this dashboard is specifically from Singapore.


### Number of room listings

```{r}
# Number of room listings
number_of_listings <-
  listing %>%
  select(id) %>%
  distinct() %>%
  count()
valueBox(number_of_listings[[1]], caption = "Number of Listings", icon = "fa-tag", color = "success")
```

### Number of hosts

```{r}
# Number of hosts
number_of_hosts <- 
    host_info %>% 
    select(host_id) %>% 
    count()
valueBox(number_of_hosts[[1]], caption = "Number of Hosts", icon = "fa-home")
```


### Number of reviews

```{r}
number_of_reviews <- listing %>% 
  select(review_scores_rating) %>%
  drop_na() %>% 
  count()
valueBox(number_of_reviews[[1]], caption = "Number of Reviews", icon = "fa-thumbs-up", color = "info")
```